%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
\usepackage{lipsum}
\usepackage[none]{hyphenat}
\usepackage[1]{pagesel}
\linespread{1}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]
\usepackage[T1]{fontenc}
%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
%% Color for highlight
\definecolor{awesome}{HTML}{000000}%Yellow
%% Colors for text
\definecolor{darktext}{HTML}{000000} %green
\definecolor{text}{HTML}{000000} % pink
\definecolor{graytext}{HTML}{000000} % red
\definecolor{lighttext}{HTML}{000000} %blue
%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Scott} \headerlastnamestyle{Myers} \\
	\vspace{1mm}
	{\faEnvelope\ scott@scottmyers.dev} | {\faLink\ https://github.com/smyers24} | {\faLink\ https://scottmyers.dev}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{Bachelor of Science in Electrical Engineering}
	{The Pennsylvania State University}
	{University Park, PA}
	{May 2018}
	{}
\end{cventries}

\vspace{-6mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
\linespread{1.40}
	\cventry
	{Software Engineer (Full Stack)}
	{Exiger}
	{}
	{August 2020 - Present}
	{\begin{cvitems}
		\item {Design, build, and test new user facing features for financial compliance OMS platform. Duties range across the stack by leveraging C\#, ASP.NET, SQL Server, Javascript, Jenkins, and more. Regularly collaborate with stakeholders to ensure optimal user experience.}
		\item {Monitor system health through logging and monitoring tools. Quickly resolve issues and optimize code/queries to minimize resource requirements. }
		\item {Identify and create automation for repetitive work, reducing engineering time from 2+ hours to several seconds in some instances.}
		\item {Ensure code is stable and well-tested during development. Created unit test framework to reduce test creation/run time by 50\%.}
		\item {Design and create REST API routes for customer integration. Update documentation accordingly.}
		\item {Establish and support RabbitMQ topology to pass messages between services.}
		\item {Write and optimize SQL queries to fulfill ad-hoc customer requests and business requirements.}
		\item {Peer review code, lead and participate in design discussions, and research/implement optimal architecture per team's vision.}
		\end{cvitems}}
	\cventry
	{Software Engineer}
	{QorTek Inc.}
	{}
	{June 2018 – August 2020}
	{\begin{cvitems}
		\item {Lead the development of a closed-loop acoustics processing system in C\# utilizing asynchronous programming and custom data visualization methods with the .NET framework. The system can also automate tests and process real-time data for the user.}
		\item {Designed and implemented a low latency, high throughput streaming protocol for use in time-sensitive applications. Utilized the protocol with a custom multithreaded streaming application.}
		\item {Create and maintain C\# class library of math algorithms, backend data visualization, framework enhancements, and more. Lead efforts and discussions about standardization and scalability of codebase.}
		\item {Designed, tested, and verified scripts that measure system health for irregularities to identify critical bugs and aid in their resolution.}
		\end{cvitems}}
	\cventry
	{Test and Automation Engineering Intern}
	{Solid State Ceramics}
	{}
	{August 2017 – May 2018}
	{\begin{cvitems}
		\item {Independently created automated ceramic piezoelectric transformer characterization program using LabVIEW. The ability to automate this process has saved the manufacturer hundreds of hours of employee labor.}
		\end{cvitems}}
	\cventry
	{Engineering Intern}
	{QorTek Inc.}
	{}
	{May 2017 – August 2017}
	{\begin{cvitems}
		\item {Designed and tested attitude control system for small satellites using C\#. Controlled hardware via micro-controller, which had data live-streamed to it via Bluetooth API. This program led to the successful validation of critical project goals.}
		\end{cvitems}}
\end{cventries}

\vspace{-5mm}
\cvsection{Skills}

\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Languages / Tech:  & {\skill{ C\#, JavaScript, HTML, ASP.NET, SQL}} \\
		Software:  & {\skill{ Visual Studio, SSMS, IIS, RabbitMQ, Jenkins, Datadog}} \\
		Computer Science:  & {\skill{ Rest API, OOP Principles, Data Structures, Algorithms}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-10mm}
\cvsection{Projects}
\begin{cventries}
	\cventry
	{Desktop application to manage players stats, dice rolls, and inventory. Code managed and documented on GitHub. New features are added by talking with players on a weekly basis during campaign sessions. Persistent game data structures allows players to easily save their data.}
	{Dungeons and Dragons Hub}
	{C\#, Windows Forms}
	{https://github.com/smyers24/DnD-Hub-V2}
	{}

\end{cventries}
\end{document}